\documentclass{article}
\usepackage{bubblecv}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\cvmainspacing{0.25}
\cvsidebarspacing{0.3}
\cvcolumnratio{0.63}
\definecolor{cvprimarycolor}{RGB}{20, 20, 20}
\usepackage{ragged2e}
%\usepackage{microtype}

\justifying
\sloppy
\tolerance=500
\hyphenpenalty=10000
\emergencystretch=3em

\begin{document}

\begin{cv}[avatar]{Gusev Egor Dmitrievich}{Student}

\cvsection[summary]{Profile}  
Second-year student at Heriot Watt University in Dubai, pursuing a Master of Arts in International Business Management. Simultaneously, a first-year student in Computer Science and Data Analysis at the Higher School of Economics, Russia. Deeply engaged in economics, IT, and principles of efficiency improvement. Dedicated to continuously developing skills and expanding knowledge in multiple fields.


\cvsection[work]{Work Experience}  

\begin{cvevent}[2022][2021]
    \cvname{Economics Assistant}
    \cvdescription{'Algorithm of Success', Russia}
    \begin{itemize}
        \item Developed economics lessons and activities in collaboration with the teacher.
        \item Evaluated student work and provided constructive feedback.
        \item Organized and conducted seminars to improve understanding of key economic concepts.
    \end{itemize}
\end{cvevent}

\begin{cvevent}[2022][2022]
    \cvname{Participant of a scientific project}
    \cvdescription{'Algorithm of Success', Russia}
    \begin{itemize}
        \item Developed 'Automatic Grade Analyzer' to improve academic performance of students.
        \item Conducted research, analyzed data, and presented results to teachers and peers.
    \end{itemize}
\end{cvevent}

\cvsection[education]{Education and Extracurricular Activities}

\begin{cvevent}[2024][2022]
	\cvname{Heriot Watt University (Dubai)}
	\cvdescription{Master of Arts in International Business Management, Second Year}
\end{cvevent}

\begin{cvevent}[2024][2022]
	\cvname{Higher School of Economics (Russia)}
	\cvdescription{Bachelor in Computer Science and Data Analysis, First Year}
\end{cvevent}

\begin{cvevent}[2022][2020]
	\cvname{OAOO OK 'Algorithm of Success' (Russia)}
	\cvdescription{Graduated with a Gold Medal}
	\textbf{Main courses and projects:}
	\begin{itemize}
		\item Analysis of the efficiency of green business.
		\item Essay on IT privacy research.
		\item Research on Nikolai Kondratiev's economic waves.
	\end{itemize}
\end{cvevent}

\begin{cvevent}[2021][2022]
	\cvname{Captain of the "What? Where? When?" team}
	\begin{itemize}
		\item Led the team to 3rd place at the Youth World Cup.
		\item Organized and coordinated team strategies.
		\item Demonstrated leadership and team interaction skills.
	\end{itemize}
\end{cvevent}



\cvsidebar 

\cvsection[contact]{Contacts}  

\begin{cvitem}[Envelope][0.6]
    \textbf{Email}\\
    \href{mailto:egor@geese.ru}{\texttt{egor@geese.ru}}
\end{cvitem}

\cvseparator[3]
\begin{cvitem}[Phone][0.6]
    \textbf{Phone}\\
    \href{tel:+971585191190}{\texttt{+971585191190}}
\end{cvitem}

\cvsection[publications]{Achievements and Awards}

\begin{cvitem}[leadership]{}
    \begin{itemize}
        \item Winner of the 'Phystech' Mathematical Tournament, 11th grade.
        \item Prize-winner at various stages of the All-Russian Olympiad in Economics, Mathematics, and Informatics, 9-11 grades.
        \item Scholarship for outstanding academic achievements in high school.
    \end{itemize}
\end{cvitem}

\cvsection[skills]{Skills} 

\begin{cvitem}
    Fluent in English and Russian
\end{cvitem}

\cvseparator
\begin{cvitem}
    Ability to work under pressure and adapt to changing circumstances
\end{cvitem}

\cvseparator
\begin{cvitem}
    High level of proficiency in mathematics and literacy
\end{cvitem}

\cvseparator
\begin{cvitem}
    Proficient in Microsoft Office Suite (Word, Excel, PowerPoint) and IT skills
\end{cvitem}

\cvsection[languages]{Languages}  
\cvskill{English}{Advanced}{1.0}
\cvskill{Russian}{Native}{1.0}
\cvskill{Spanish}{Beginner}{0.1}

\end{cv}

\vfill % Use this to push the following lines to the bottom of the page
\hrule % Draw a horizontal line
\begin{center} % Begin centering
\tiny % Make the font even smaller
I agree to the processing of my personal data provided in this document for the implementation of the recruitment process in accordance with the Federal Law of the Russian Federation of July 27, 2006 N 152-FZ "On Personal Data".
\end{center} % End centering

\end{document}
